Dark matter halo concentrations with a bayesian approach

### 2014-05-27 paper/article.tex
new figure + new paragraph

The method we use to generate the halos is based on the integrated
mass profile. Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle such that the total mass is one). Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that
\begin{equation}
m(<r;c)-k \cdot \delta m 
\end{equation}
is zero using Ridders' method. This value of $r$ will be the radius of the $k$th particle of the generated halo, then polar and azimuthal angles $\theta$ and $\phi$ are generated randomly. Finally these three coordinates are transformed into cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$ times in order to generate the $x,y,z$ coordinates for each particle.

@@

\subsection{Mock Halos}
\label{sec:results_mocks}
\begin{figure}[H]
\caption{FIXME: Test results}
\end{figure}

>>>>

The method we use to generate the halos is based on the integrated
mass profile. Given the number of particles $n$ and the concentration
$c$ we define the mass element as $\delta m = 1/n$ (this corresponds
to the mass of each particle such that the total mass is one). Then
for each number $k$ from $1$ to $n$ we find the value of $r$ such that
the difference 
%
\begin{equation}
m(<r;c)-k \cdot \delta m 
\end{equation}
%
is zero using Ridders' method. This value of $r$ is the radius of
the $k$th particle of the generated halo, then polar and azimuthal
angles $\theta$ and $\phi$ are randomly generated. Finally these three
coordinates are transformed into cartesian coordinates
$(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$
times in order to generate the $x,y,z$ coordinates for each particle.

@@

\subsection{Mock Halos}
\label{sec:results_mocks}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{percentual_diff.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with a different number of particles, $N$.
    \label{fig:results_mocks}}
\end{figure}

In Figure \ref{fig:results_mocks} we show the integrated distribution
percentual difference between the concentration measured with our
fitting method $c_{out}$ in comparison with the concentration used to
generate the mock halos, $c_{in}$, $D=(c_{in}-c_{out})/c_{in}$.
